---
title: "Initial scraping practice"
output: html_notebook
---

```{r}
library(xml2)
library(plyr)
library(rvest)
library(tidyverse)
library(readr)
```

```{r}
parfum <- read_html("https://www.wikiparfum.com/en/fragrances/wood-sage-sea-salt-2024")
```

```{r}
parfum %>% 
  html_element(".flex-wrap") %>% 
  html_children() %>% 
  html_text()
```
```{r}
fraglist <- read_xml("https://www.wikiparfum.com/fragrances_sitemap_en_0.xml")

fraglist %>% 
  xml_children()
```



```{r}
fragranceURLs <- c("https://www.wikiparfum.com/en/fragrances/wood-sage-sea-salt-2024")

fragrence <- tibble(URL = fragranceURLs) %>% 
  mutate(HTML = map(URL, read_html))
```

```{r}
test <- fragrence %>% 
  # almost correct element
  mutate(frag.name = map(HTML, ~.x %>% 
                     html_element(".xl\\:col-start-5") %>% 
                     html_children() %>% 
                            html_text())) %>% 
                           #somehow need to remove brand from name
  # correct element
  mutate(ingredients = map(HTML, ~ .x %>% 
                              html_element(".flex-wrap") %>% 
                              html_children() %>% 
                              html_text())) %>% 
# correct element, need to remove "info"
mutate(price = map(HTML, ~.x %>% 
                     html_element(".text-16.flex.gap-2") %>% 
                            html_text())) %>%
  
 # almost correct element. needs some tidying
mutate(olfactive.class = map(HTML, ~.x %>% 
                     html_element(".p-3") %>% 
                     html_children() %>% 
                            html_text())) %>% 
# incorrect elemnt
mutate(world.clasif = map(HTML, ~.x %>% 
                     html_element(".text-16") %>%
                       html_children() %>%
                            html_text())) %>% 
#Correct path!
  mutate(description = map(HTML, ~.x %>% 
                     html_element(".pb-3") %>% 
                            html_text())) %>% 
 #correct path
   mutate(origin = map(HTML, ~.x %>% 
                     html_element(".py-5") %>% 
                            html_text())) %>% 
  # correct path 
  mutate(gender = map(HTML, ~.x %>% 
                     html_element(".border-gold200:nth-child(2)") %>% 
                            html_text())) %>% 
  # correct path
    mutate(year = map(HTML, ~.x %>% 
                     html_element(".border-gold200:nth-child(3)") %>% 
                            html_text())) %>% 
  # correct path
    mutate(concepts = map(HTML, ~.x %>% 
                     html_element(".border-gold200~ .border-gold200+ .border-gold200") %>% 
                            html_text())) %>% 
  # incorrect path
  mutate(perfumer = map(HTML, ~.x %>% 
                     html_element(".pt-5.gap-4") %>% 
                            html_text()))  
  
test$perfumer
```

# Web-scraping the J! Archive

Let's say we want to understand how _this_ & _these_ are used in _Jeopardy!_ clues.
We can scrape the fabulous [J! Archive](https://www.j-archive.com/index.php).

We'll start with a single _Jeopardy!_ game from August 2021...

```{r}
j7117 <- read_html("https://www.j-archive.com/showgame.php?game_id=7117")
```

...and try to write a function `get_clues()` that takes as input the game's `game_id` (from the J! Archive) and returns a dataframe like the following:

```{r}
read_csv("jeopardy7117-clues.csv", col_types="cciic")
```

# Multiple pages

Now let's apply `clue_df()` to multiple pages.

```{r}
season37 <- read_html("https://www.j-archive.com/showseason.php?season=37")
```



# Session info

```{r}
sessionInfo()
